Working title: Mirkovi\'c--Vybornov fusion in Beilinson--Drinfeld Grassmannian

### 2020-12-24 examples.tex
more lattice descriptions
corrected typo in example 7

    In $\Gr$ the element $g$ defines the lattice 
    \[
        gL_0 = \CC[t]\langle
        (t-s)t^3e_1 - bt e_2 - ce_3 , (t-s)te_2 - de_3, te_3 
        \rangle
    \]
    and computing the matrix of the action of $t$ on the quotient $L_0/L$ in the basis 
    \[
    \{
        [e_1],[te_1],[t^2e_1],[t^3e_1],[e_2],[te_2],[e_3]
    \}    
    \]
    recovers $X$ up to a transpose of course.

@@

    Next let's find $L_0 = L\otimes\CC\xt[t-s]$. 
    \[
        L_0 = \CC[t]\langle
        t^3 e_1 - bte_2 - ce_3, te_2 - de_3 , te_3 
        \rangle 
    \]
    so 
    \[
    \left[t\big|_{L_0/L_s}\right]_{\{[e_1],[te_1],[t^2e_1],[e_2],[e_3]\}} = \begin{bmatrix}
        0 \\
        1 & 0 \\
        0 & 1 & 0 \\
          & & & 0 \\
          & & & d & 0  
    \end{bmatrix}
    \]
    which has block type $\mu_1$ and Jordan type $\lambda_1$ as expected. 
\end{example}

>>>>

    In $\Gr$ the element $g$ defines the lattice 
    \[
        gL_0 = \CC[t]\langle
        (t-s)t^3e_1 - (a+bt) e_2 - ce_3 , (t-s)te_2 - de_3, te_3 
        \rangle
    \]
    and computing the matrix of the action of $t$ on the quotient $L_0/L$ in the basis 
    \[
    \{
        [e_1],[te_1],[t^2e_1],[t^3e_1],[e_2],[te_2],[e_3]
    \}    
    \]
    recovers $X$ up to a transpose of course.

@@

    Next let's find $L_0 = L\otimes\CC\xt[t-s]$. 
    \[
        L_0 = \CC[t]\langle
        t^3 e_1 - bte_2 - ce_3, te_2 - de_3 , te_3 
        \rangle 
    \]
    so 
    \[
    \left[t\big|_{L_0/L_s}\right]_{\{[e_1],[te_1],[t^2e_1],[e_2],[e_3]\}} = \begin{bmatrix}
        0 \\
        1 & 0 \\
        0 & 1 & 0 \\
          & & & 0 \\
          & & & d & 0  
    \end{bmatrix}
    \]
    which has block type $\mu_1$ and Jordan type $\lambda_1$ as expected!
\end{example}
